---
title: "Interactions_AllFigs"
author: "Biraj Adhikari"
date: "4/9/2021"
output: html_document
---

This is the RMD file that has codes for the entire figures I have used for the Interactions paper, arranged according to figures in the text. 

## Installing Libraries:
```{r}
#Package names
# Installing required packages if not installed yet
if("devtools" %in% rownames(installed.packages())   == FALSE){
  install.packages("devtools")}
library(devtools)
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("ggplot2")}
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("dplyr")}
#for radarplot
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("fmsb")}
#for heatmap
devtools::install_github("rlbarter/superheat")
#for combining base and ggplot together
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("gridBase")}
#for network
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("igraph")}
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("RColorBrewer")}
if("statnet" %in% rownames(installed.packages())   == FALSE){
  install.packages("reshape2")}
if("ggpubr" %in% rownames(installed.packages())   == FALSE){
  install.packages("ggpubr")}

```

## Adding the libraries
```{r}
library(ggplot2)
library(dplyr)
library(fmsb) # for radarplot
library(grid)
library(superheat) #for heatmap
library(gridBase) #for combining base and ggplot together
library(igraph)
library(RColorBrewer)
library(reshape2) #for figure 5
library(ggpubr) #for ggarrange (to combine multiple figures together)
```
## FIGURE 3: Plots for Radar Diagrams: Setting up

```{r}
#MOUNTAIN
rad_m = read.csv('Radar_mountain.csv', header = TRUE, sep = ",")

#adding row names
rownames(rad_m) = "Mountain"

#adding maximum and minimum
rad_m = rbind(rep(1,17), rep(-1,17), rad_m)

#HILL
rad_h = read.csv('Radar_hill.csv', header = TRUE, sep = ",")

#adding row names
rownames(rad_h) = "Hills"

#adding maximum and minimum
rad_h = rbind(rep(1,17), rep(-1,17), rad_h)

#TERAI
rad_t = read.csv('Radar_terai.csv', header = TRUE, sep = ",")


#adding row names
rownames(rad_t) = "Terai"

#adding maximum and minimum
rad_t = rbind(rep(1,17), rep(-1,17), rad_t)

#NEPAL
rad_n = read.csv('Radar_nepal.csv', header = TRUE, sep = ",")

#adding row names
rownames(rad_n) = "Nepal"

#adding maximum and minimum
rad_n = rbind(rep(1,17), rep(-1,17), rad_n)
```
## Making Figure 3

```{r}
#saving to png
png(filename = "radar_nepal.png",            
 width = 1600,        
  height = 1400,
  res = 300,  
  )

#Arranging rows and columns
par(mfrow=c(2,2))

#Making the plots
#MOUNTAIN
par(mar = c(0.5, 0.5, 1.5, 0.5))
radarchart(rad_m, 
           #defining the axis
           axistype = 1, seg = 2,caxislabels=c("Negative",0,"Positive"),axislabcol="black",
           
           #defining plot type
           plwd = 1,plty = 1,pcol = rgb(255, 217, 47, 150,maxColorValue = 255), pfcol = rgb(255, 217, 47, 75,maxColorValue = 255),
           
           #defining font sizes
           vlcex = 0.5, calcex = 0.6,
           
           #defining the net
           cglcol = "grey",cglty=1,   cglwd=2,
           title = "Mountain", cex.main = 0.8)

#HILL
 radarchart(rad_h, 
           #defining the axis
           axistype = 1, seg = 2,caxislabels=c("Negative",0,"Positive"),axislabcol="black",
           
           #defining plot type
           plwd = 1,plty = 1,pcol = rgb(141, 160, 203, 150,maxColorValue = 255), pfcol = rgb(141, 160, 203, 75,maxColorValue = 255),
           
           #defining font sizes
           vlcex = 0.5, calcex = 0.6,
           
           #defining the net
           cglcol = "grey",cglty=1,   cglwd=2,
           title = "Hill", cex.main = 0.8)
 
#TERAI
radarchart(rad_t, 
           #defining the axis
           axistype = 1, seg = 2,caxislabels=c("Negative",0,"Positive"),axislabcol="black",
           
           #defining plot type
           plwd = 1,plty = 1,pcol = rgb(252, 141, 98, 150, maxColorValue = 255), pfcol = rgb(252, 141, 98, 75, maxColorValue = 255),
           
           #defining font sizes
           vlcex = 0.5, calcex = 0.6,
           
           #defining the net
           cglcol = "grey",cglty=1,   cglwd=2,
           title = "Terai", cex.main = 0.8)
#NEPAL
radarchart(rad_n, 
           #defining the axis
           axistype = 1, seg = 2,caxislabels=c("Negative",0,"Positive"),axislabcol="black",
           
           #defining plot type
           plwd = 1,plty = 1,pcol = rgb(128, 0, 0, 150, maxColorValue = 255), pfcol = rgb(128, 0, 0, 75, maxColorValue = 255),
           
           #defining font sizes
           vlcex = 0.5, calcex = 0.6,
           
           #defining the net
           cglcol = "grey",cglty=1,   cglwd=2,
           title = "Nepal", cex.main = 0.8)

dev.off()

```

## FIGURE 4b: Distribution of interactions between forest cover and other SDGs for Nepal and its three ecological zones for 2010. 

```{r}
fig4 = read.csv('Figure4.csv', header = TRUE, sep = ",")

fig4$Region = factor(fig4$Region, levels = c("Nepal", "Mountain", "Hills", "Terai"))
fig4$Interaction = factor(fig4$Interaction, levels = c("Unspecified", "Tradeoff", "Synergy"))

panel_fig4 = ggplot(fig4, aes(fill = Interaction,y = percent, x = Region, label = scales::percent(percent))) + geom_bar(position = "stack", stat = "identity") + 
  scale_fill_manual(values = c("#ffff99" , "#fdc086", "#7fc97f")) +
  theme(axis.text.x = element_text(size = 8)) +
  scale_y_continuous(labels = function(x) paste0(x*100, "%")) + 
  labs(title = "(b) Proportion of interactions between forest cover and other\nSDGs disaggregated by ecozones", y = "", x = "") + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  theme(plot.title = element_text(size = 12),
        axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.text = element_text(size = 12),
        legend.title = element_blank(),
        panel.background = element_rect(fill = "white"))
  

panel_fig4
```

##FIGURE 4a: Standardized Time-series graph of SDG 15 Indicators
```{r}
alldat = read.csv('Figure5.csv', header = TRUE, sep = ",")

Year = as.integer(alldat$Year)
alldat = alldat[,-1]
alldat.z = scale(alldat)
alldat.z = cbind(Year = Year, alldat.z)
alldat.z = as.data.frame(alldat.z)
mdf = reshape2::melt(alldat.z, id.var = "Year")

target1 = c("pr_forest", "kba_f", "kba_m", "redlist", "bio_aid" )
mdf2 = filter(mdf, variable %in% target1)

panel_fig5 = ggplot(data = mdf2, aes(x = Year, y = value, colour = variable, label = variable)) + geom_point() + geom_line(size = 1.3) + scale_color_manual(values = c("#008000", "#003366", "#b36b00","#800000",  "#330066")) + scale_x_continuous(limits = c(2000,2020)) + labs(color = "SDG 15 indicators") + 
  
  labs (x = "", y = "", title = "(a) Standardized time-series graph of SDG 15 indicators") +
 theme(plot.title = element_text(size = 12),
       axis.text.x = element_text(size = 11),
       legend.text = element_text(size = 12),
        
      panel.background = element_rect(fill = "white"), axis.text.y = element_blank())

panel_fig5

```

##FIGURE S1: Heat map of correlations between SDG 15 indicators and other SDG indicators showed that forest cover interacted negatively with many indicators
```{r}
heatdat = read.csv('Figure6.csv', header = TRUE, sep = ",")
#saving the row names
rnames <- heatdat[,1]

#converting the data to matrix format (except the first column which is the name of row)
m_heatdat = data.matrix(heatdat[,2:ncol(heatdat)])

#assigning rownames from rnames variable
rownames(m_heatdat) = rnames


#making a png file
png(filename = "heatmaps_correlation.png",            
  width = 1500,        
  height = 3000,
  res = 300,  
  
  ) 


#plotting the heatmap
superheat(m_heatdat, 
          left.label.text.size = 2.5, left.label.size = 0.2, 
          bottom.label.text.size = 3, bottom.label.size = 0.12, bottom.label.text.angle = 90,
          heat.pal = c("#d7191c", "#ffffbf","#1a9641"),
          title = "Correlation heatmap", title.size = 4, title.alignment = "center",
          row.title = "Other SDG targets", row.title.size =7,
          column.title = "SDG 15 targets", column.title.size = 7,
          grid.hline.col = "white",
          grid.vline.col = "White",
          grid.vline.size = 0.5,
          grid.hline.size = 1,
          legend.vspace = 0.05
                    )
```

##FIGURE 4c: Proportion of synergy, tradeoff and unspecified interactions disaggregated into individual SDG 15 indicator
```{r}

alldat = read.csv('Figure7.csv', header = TRUE, sep = ",")

alldat$indicator = factor(alldat$indicator, levels = c("pr_forest", "kba_f", "kba_m", "redlist", "bio_aid"))
alldat$interaction = factor(alldat$interaction, levels = c("Unspecified", "Tradeoff", "Synergy"))


panel_fig7 = ggplot(alldat, aes(fill = interaction,y = count, x = indicator, label = scales::percent(count))) + geom_bar(position = "stack", stat = "identity") + 
  scale_fill_manual(values = c("#ffff99" , "#fdc086", "#7fc97f")) +
  theme(axis.text.x = element_text(size = 8)) +
  labs(y = "", x = "", title = "(c) Proportion of interactions between SDG 15 indicators and\nother SDGs") + 
  scale_y_continuous(labels = function(x) paste0(x*100, "%")) + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) + 
 
   theme(plot.title = element_text(size = 12),
         axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.text = element_text(size = 12),
        legend.title = element_blank(),
      panel.background = element_rect(fill = "white"))
  
panel_fig7
```

##Combining figures 4, 5 and 7 together: Figure 4
```{r}

ggarrange(panel_fig5, ggarrange(panel_fig4, panel_fig7, nrow = 1, ncol = 2, common.legend = TRUE, legend  = "bottom"), nrow = 2, ncol = 1)

ggsave("Panel_fig4.png", dpi = 300, height = 200 , width = 280, units = "mm")

```



##FIGURE 5: An indicator level network diagram of SDGs
```{r}
temp_netdat = read.csv('Figure8.csv', header = TRUE, row.names = 1, sep = ",")

#creating network
network <- graph_from_adjacency_matrix(as.matrix(temp_netdat), mode = "undirected", weighted = "interaction", diag = FALSE)

#creating a png file
png(filename = "TempNetwork.png",            
width = 2100,        
height = 1860,
res = 300, 
 )


#giving width to edges according to their magnitudes
E(network)$width = abs(E(network)$interaction)

#colouring edges according to synergy or tradeoff
E(network)$color[E(network)$interaction == 1] <- '#5ab4ac'
E(network)$color[E(network)$interaction == -1] <- '#d8b365'

#colouring nodes based on which SDG goal they belong to
V(network)$color[1:5] <- '#e5243b' #SDG 1
V(network)$color[6:11]<- '#dda63a' #SDG 2
V(network)$color[12:31]<-'#4c9f38' #SDG 3
V(network)$color[32:35]<-'#c5192d' #SDG 4
V(network)$color[36] <- '#ff3a21'  #SDG 5
V(network)$color[37:41]<-'#26bde2' #SDG 6
V(network)$color[42:46]<-'#fcc30b' #SDG 7
V(network)$color[47:50]<-'#a21942' #SDG 8
V(network)$color[51:55]<-'#6e8255' #SDG 9
V(network)$color[56:58]<-'#dd1367' #SDG 10
V(network)$color[59:61]<-'#fd9d24' #SDG 11
V(network)$color[62]<-'#bf8b2e' #SDG 12
V(network)$color[63]<-'#3f7e44' #SDG 13
V(network)$color[64:68]<-'#56c02b' #SDG 15
V(network)$color[69:71]<-'#00689d' #SDG 16
V(network)$color[72:81]<-'#19486a' #SDG 17

#renaming vertices
vname = read.csv('indicator_sdg.csv', header = TRUE, sep = ",")
V(network)$name = as.character(vname$Indicator)

#greys <- brewer.pal(3, "Greys")
#greens <- brewer.pal(3, "Greens")
#E(network)$color[between(E(network)$interaction,-1,-0.98)] = greys[2]
#E(network)$color[between(as.numeric(E(network)$interaction),-0.95,-0.87)] = reds[1] 
#E(network)$color[between(as.numeric(E(network)$interaction),0.98, 1)] = greens[2]
#E(network)$color[between(E(network)$interaction,0.86,0.94)] = greens[1]



#providing a vector to scale the size of the vertices
V(network)$eigenv <- eigen_centrality(network, weights = as.numeric(abs(E(network)$interaction)))$vector #the size of the vertices will be determined by the eigenvector centrality

#removing nodes whose eigenvector centrality is less than 0.1
network = delete_vertices(network, V(network)[V(network)$eigenv < 0.1])

#margins
par(mar = c(1,1,1,1))

#plotting the network
x = plot(network,
    
     vertex.size = (V(network)$eigenv+0.8)^4,
     vertex.label.cex = 0.5, #size of the labels
     vertex.label.color = 'black',
    #vertex.label.dist = -1.7, #spacing between label and vertices
     vertex.label.font = 1, #making the label bold
      edge.curved = 0.2,
     layout = layout.circle,
    
    
)


```


##FIGURE 6: Network diagram for interactions between SDG 15 indicators and the other SDGs
```{r}
temp_net2 = read.csv('Figure9.csv', header = TRUE, row.names = 1, sep = ",")

#creating network
network2 <- graph_from_incidence_matrix(as.matrix(temp_net2), weighted = "interaction")

#creating a png file
png(filename = "TempNetwork2.png",            
width = 1200,        
height = 1200,
res = 300, 
  )


#giving width to edges according to their magnitudes
E(network2)$width = abs(E(network2)$interaction)*10

#colouring edges according to synergy or tradeoff
E(network2)$color[E(network2)$interaction > 0] <- '#5ab4ac'
E(network2)$color[E(network2)$interaction < 0] <- '#d8b365'

V(network2)$color[1] <- '#e5243b' #SDG 1
V(network2)$color[2]<- '#dda63a' #SDG 2
V(network2)$color[3]<-'#4c9f38' #SDG 3
V(network2)$color[4]<-'#c5192d' #SDG 4
V(network2)$color[5] <- '#ff3a21'  #SDG 5
V(network2)$color[6]<-'#26bde2' #SDG 6
V(network2)$color[7]<-'#fcc30b' #SDG 7
V(network2)$color[8]<-'#a21942' #SDG 8
V(network2)$color[9]<-'#6e8255' #SDG 9
V(network2)$color[10]<-'#dd1367' #SDG 10
V(network2)$color[11]<-'#fd9d24' #SDG 11
V(network2)$color[12]<-'#bf8b2e' #SDG 12
V(network2)$color[13]<-'#3f7e44' #SDG 13
V(network2)$color[16:20]<-'#56c02b' #SDG 15
V(network2)$color[14]<-'#00689d' #SDG 16
V(network2)$color[15]<-'#19486a' #SDG 17


#greys <- brewer.pal(3, "Greys")
#greens <- brewer.pal(3, "Greens")
#E(network)$color[between(E(network)$interaction,-1,-0.98)] = greys[2]
#E(network)$color[between(as.numeric(E(network)$interaction),-0.95,-0.87)] = reds[1] 
#E(network)$color[between(as.numeric(E(network)$interaction),0.98, 1)] = greens[2]
#E(network)$color[between(E(network)$interaction,0.86,0.94)] = greens[1]



#providing a vector to scale the size of the vertices
V(network2)$eigenv <- eigen_centrality(network2, weights = as.numeric(abs(E(network2)$interaction)))$vector #the size of the vertices will be determined by the eigenvector centrality



#margins
par(mar = c(1,1,1,1))

#setting angle (in gradients) and position of vertex (so that they dont overlap within the vertex)

angle <- c(rep(1,20))
for (i in 1:20){
  angle[i] <- 0.314 * (21-i) 
} #the loop was applied so that the labels are printed outside the network

x = c(2.8,3.8,3.2,2.8,1,1.2,2,1,1.8,2.8,2.8,1.8,1.2,1.3,1.9,2.7,2.3,2.8,2.8,2.7) #to adjust size of labels according to vertex size


#plotting the network
plot(network2,
    
     vertex.size = V(network2)$eigenv*25,
     vertex.label.cex = 0.6, #size of the labels
     vertex.label.color = 'black',
     vertex.label.dist = x,
     vertex.label.font = 2, #making the label bold
     edge.curved = 0.1,
     vertex.label.degree = angle,
     layout = layout.circle,
     vertex.frame.color = V(network2)$color
)
```

